
---
title: "Data Science Notebook"
author: "Author Name"
date: "2024-10-16"
output: html_document
---

# Exercise 2 - Title of the Notebook
This is the **Data Science Notebook** created as part of an exercise.

# Exercise 3 - Introduction
In this notebook, we will cover some basic concepts related to Data Science, including languages, libraries, and tools commonly used in the field.

# Exercise 4 - Data Science Languages
Some of the popular languages used in Data Science are:
- Python
- R
- SQL
- Julia
- Java

# Exercise 5 - Data Science Libraries
Some of the widely used libraries in Data Science are:
- NumPy
- Pandas
- Matplotlib
- TensorFlow
- scikit-learn

# Exercise 6 - Data Science Tools
| Tool               | Purpose                        |
|--------------------|--------------------------------|
| Jupyter Notebooks  | Interactive Coding Environment |
| RStudio            | R IDE for Data Analysis        |
| Apache Hadoop      | Distributed Data Processing    |
| Tableau            | Data Visualization             |
| Apache Spark       | Big Data Analytics             |

# Exercise 7 - Arithmetic Expression Examples
Below are some examples of simple arithmetic expressions.

# Exercise 8 - Multiply and Add Numbers
```{r}
# Multiplication and Addition
result <- (3 * 4) + 5
result
```

# Exercise 9 - Convert Minutes to Hours
```{r}
# Convert 120 minutes to hours
minutes <- 120
hours <- minutes / 60
hours
```

# Exercise 10 - Objectives
The objectives of this notebook are:
- Understand basic Data Science concepts
- Learn about commonly used tools, languages, and libraries
- Practice arithmetic operations in R

# Exercise 11 - Author
**Author:** Your Name

# Exercise 12 - GitHub
This notebook can be shared through GitHub.

# Exercise 13 - Screenshot
Include a screenshot of the first page of the notebook.

